Notes on the low density parameters in {\tt MAESTRO}

### 2010-09-14 docs/lo_density/lo_density.tex
add a discussion of buoyancy_cutoff_density

@@

@@

@@

>>>>

The {\tt anelastic\_cutoff} is the density below which we modify the constraint.

@@

The {\tt base\_cutoff\_density} is the lowest density that we model.

@@

The burning cutoff determines where we call the reaction network to
get the nuclear energy generation rate and composition changes.  For
densities below the burning cutoff, we do not call the network.

@@

\section{buoyancy\_cutoff\_factor}

The {\tt buoyancy\_cutoff\_factor} is used to zero out the forcing terms
to the velocity equation at low densities.

\item In {\tt init\_base\_state} we print out the value of the
   the density at which the buoyancy cutoff would take effect,
   {\tt buoyancy\_cutoff\_factor * base\_cutoff\_density}.

\item In {\tt mk\_vel\_force}, we zero out {\tt rhopert}, the
   perturbational density used in computing the buoyancy force,
   if $\rho < \mathtt{buoyancy\_cutoff\_factor * base\_cutoff\_density}$.

\item In {\tt mk\_vel\_force}, for spherical problems, we 
   zero out {\tt centrifugal\_term}, the centrifugal force for
   rotating stars, if $\rho < \mathtt{buoyancy\_cutoff\_factor *
   base\_cutoff\_density}$.
